The imprint of global magma oceans on exoplanet demographics

### 2023-03-11 src/tex/ms.tex
discuss Nautilus Observatory concept

Taken together, \plato\ appears to be the most promising exoplanet mission for an empirical confirmation or falsification of the runaway greenhouse transition at this time.

>>>>

Looking further ahead, the Nautilus Space Observatory concept~\citep{Apai2019} represents a statistical mission able to provide precise radius measurements of a large sample of small exoplanets.
It employs a swarm of large telescopes using ultralight diffractive-refractive optical elements~\citep{Milster2020} with the primary goal to study the atmospheres of transiting exoplanets.
Operating in an array mode, Nautilus would achieve the equivalent light-collecting area of a \SI{50}{\meter} telescope.
Its expected \SI{1}{\ppm} photometric precision~\citep{Apai2022} would enable precise radius measurements of a large sample, also through a low number of required visits per object.
If realized, Nautilus will be a valuable instrument for characterizing the runaway greenhouse transition.

As for exoplanets missions in their implementation phase, \plato\ overall appears to be the most promising mission for an empirical confirmation or falsification of the runaway greenhouse transition at this time.
